Anna Analysis with John

### 2024-03-26 Anna qPCR data/AnnaThesisAnalyses.Rmd
aleah data

qPCR = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/Anna%20qPCR%20data/Anna_qPCR_allData.csv")

@@

pepck = qPCR[qPCR$Primer == "Pepck-1",]
pepck = pepck[pepck$Censor != 'yes',]
pepck = pepck[pepck$Concentration == 5,]
pepck = pepck[pepck$Efficiency == 'no',]

@@

idgf = qPCR[qPCR$Primer == "Idgf6",]
idgf = idgf[idgf$Censor != 'yes',]
idgf = idgf[idgf$Concentration == 5,]
idgf = idgf[idgf$Efficiency == 'no',]

@@

plotdata = mean.pcb
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "cornflowerblue"
main = "PCB"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.ldh
keep = T
color = "gold"
main = "LDH"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.pdh
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "brown"
main = "PDH"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.p53
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "black"
main = "p53"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.PyK
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "deeppink"
main = "PyK"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.idgf
keep = T
color = "limegreen"
main = "idgf6"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

plotdata = mean.pepck
keep = T
color = "orange"
main = "PEPCK-1"
plotdata = plotdata[keep,]
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

>>>>

library(reshape2)
qPCR = read.csv("https://raw.githubusercontent.com/johncsantiago/WhartonLab/master/Anna%20qPCR%20data/Anna_qPCR_allData.csv")

@@

pepck = qPCR[qPCR$Primer == "Pepck1",]
pepck = pepck[pepck$Censor != 'yes',]
pepck = pepck[pepck$Concentration == 5,]
pepck = pepck[pepck$Efficiency == 'no',]

@@

idgf = qPCR[qPCR$Primer == "IDGF6",]
idgf = idgf[idgf$Censor != 'yes',]
idgf = idgf[idgf$Concentration == 5,]
idgf = idgf[idgf$Efficiency == 'no',]

@@

plotdata = mean.pcb
color = "cornflowerblue"
main = "PCB"

plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

```{r echo = F}
plotdata = plotdata[order(plotdata$Rep),]

G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
                plotdata[plotdata$Sample == "G85R", 'Rep'])
WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
                plotdata[plotdata$Sample == "WT", 'Rep'])
RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
                plotdata[plotdata$Sample == "RNAi", 'Rep'])

paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
                         WT = WT[unique(plotdata$Rep)],
                         RNAi = RNAi[unique(plotdata$Rep)])
row.names(paired.data) = unique(plotdata$Rep)

paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
                      'paired_p-val' = c(0,0,0))

paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]

paired.p
```

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == i, ]
  ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
  ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT']   
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

plotdata = mean.ldh
keep = T
color = "gold"
main = "LDH"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

```{r echo = F}
plotdata = plotdata[order(plotdata$Rep),]

G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
                plotdata[plotdata$Sample == "G85R", 'Rep'])
WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
                plotdata[plotdata$Sample == "WT", 'Rep'])
RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
                plotdata[plotdata$Sample == "RNAi", 'Rep'])

paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
                         WT = WT[unique(plotdata$Rep)],
                         RNAi = RNAi[unique(plotdata$Rep)])
row.names(paired.data) = unique(plotdata$Rep)

paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
                      'paired_p-val' = c(0,0,0))

paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]

paired.p
```

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(NA, length(unique(plotdata$Rep))),
                  RNAi = rep(NA, length(unique(plotdata$Rep))))

i=3
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

plotdata = mean.pdh
keep = T
color = "brown"
main = "PDH"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

```{r echo = F}
plotdata = plotdata[order(plotdata$Rep),]

G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
                plotdata[plotdata$Sample == "G85R", 'Rep'])
WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
                plotdata[plotdata$Sample == "WT", 'Rep'])
RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
                plotdata[plotdata$Sample == "RNAi", 'Rep'])

paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
                         WT = WT[unique(plotdata$Rep)],
                         RNAi = RNAi[unique(plotdata$Rep)])
row.names(paired.data) = unique(plotdata$Rep)

paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
                      'paired_p-val' = c(0,0,0))

paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]

paired.p
```

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

```
```{r echo = F}

plotdata = mean.p53
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "black"
main = "p53"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

plotdata = mean.PyK
keep = plotdata$Sample != "WT-cr 1" & plotdata$Sample != "WT-cr 2"
color = "deeppink"
main = "PyK"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

plotdata = mean.idgf
keep = T
color = "limegreen"
main = "idgf6"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

```{r echo = F}
plotdata = plotdata[order(plotdata$Rep),]

G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
                plotdata[plotdata$Sample == "G85R", 'Rep'])
WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
                plotdata[plotdata$Sample == "WT", 'Rep'])
RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
                plotdata[plotdata$Sample == "RNAi", 'Rep'])

paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
                         WT = WT[unique(plotdata$Rep)],
                         RNAi = RNAi[unique(plotdata$Rep)])
row.names(paired.data) = unique(plotdata$Rep)

paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
                      'paired_p-val' = c(0,0,0))

paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]

paired.p
```

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")

plotdata = mean.pepck
keep = T
color = "orange"
main = "PEPCK-1"

plotdata = plotdata[keep,]
plotdata$Rep = substr(plotdata$Sample, nchar(plotdata$Sample), nchar(plotdata$Sample))
plotdata$Sample[grep("WT",plotdata$Sample)] = "WT"
plotdata$Sample[grep("RNAi",plotdata$Sample)] = "RNAi"
plotdata$Sample[grep("G85R",plotdata$Sample)] = "G85R"
plotdata$Sample = factor(plotdata$Sample,
                         levels = c("WT", "G85R", "RNAi"))

@@

summary(aov(dCT ~ Sample + Rep, data = plotdata))

```{r echo = F}
plotdata = plotdata[order(plotdata$Rep),]

G85R = setNames(plotdata[plotdata$Sample == "G85R", 'dCT'],
                plotdata[plotdata$Sample == "G85R", 'Rep'])
WT = setNames(plotdata[plotdata$Sample == "WT", 'dCT'],
                plotdata[plotdata$Sample == "WT", 'Rep'])
RNAi = setNames(plotdata[plotdata$Sample == "RNAi", 'dCT'],
                plotdata[plotdata$Sample == "RNAi", 'Rep'])

paired.data = data.frame(G85R = G85R[unique(plotdata$Rep)],
                         WT = WT[unique(plotdata$Rep)],
                         RNAi = RNAi[unique(plotdata$Rep)])
row.names(paired.data) = unique(plotdata$Rep)

paired.p = data.frame('paired_t.test' = c("G85R-WT", "RNAi-WT", "G85R-RNAi"),
                      'paired_p-val' = c(0,0,0))

paired.p[1,2] = t.test(paired.data$G85R, paired.data$WT, paired = T)[3]
paired.p[2,2] = t.test(paired.data$RNAi, paired.data$WT, paired = T)[3]
paired.p[3,2] = t.test(paired.data$G85R, paired.data$RNAi, paired = T)[3]

paired.p
```

ddCT = data.frame(Rep = unique(plotdata$Rep),
                  G85R = rep(0, length(unique(plotdata$Rep))),
                  RNAi = rep(0, length(unique(plotdata$Rep))))

i=1
while(i <= length(unique(plotdata$Rep))){
  temp = plotdata[plotdata$Rep == unique(plotdata$Rep)[i], ]
  if(length(grep('G85R',temp$Sample)) & length(grep('WT',temp$Sample))){
    ddCT$G85R[i] = temp[temp$Sample == "G85R", 'dCT'] - temp[temp$Sample == "WT", 'dCT']
  }
    if(length(grep('RNAi',temp$Sample)) & length(grep('WT',temp$Sample))){
      ddCT$RNAi[i] = temp[temp$Sample == "RNAi", 'dCT'] - temp[temp$Sample == "WT", 'dCT'] 
    }
  i=i+1
}

ddCT = melt(ddCT, id.vars = "Rep", variable.name = "Sample", value.name = 'ddCT')

boxplot(ddCT$ddCT~ddCT$Sample,
     ylab = "ddCT",
     xlab = "",
     main = main,
     las = 2)

points(x = ddCT$Sample,
       y = ddCT$ddCT,
       cex = 1.5,
       pch = 21,
       bg = color,
       col = "black")
